Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-25 analysis/paper/paper.Rmd
Split N_rates into own data
Generate `tibble` object of N rates ad timing in "/data-raw"

Include `N_rates` as a `tibble` object

Document `N_rates`

Update static docs

```{r N-management, }
regulartable(N_management, col_keys = c("Nitrogen treatment",
                                        "Year", 
                                        "Total N (kg/ha)",
                                        "Basal",
                                        "Tillering",
                                        "Panicle Initiation")
             )
```

>>>>

```{r N-management, tab.cap="Nitrogen application rates for 2015 and 2016. Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N~0~), 100 kg per ha N (N~1~) and 180 kg per ha N (N~2~). In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N~3~) and 180 kg per ha N (N~4~). Treatments were applied in splits, basal, tillering and panicle initiation growth stages."}

N_rate <- xtable(N_rate) # the N_rate object is a tibble of data distributed with rice.awd.pests
N_rate <- xtable_to_flextable(x = N_rate, NA.string = "-")

N_rate <- flextable::display(
  N_rate,
  i = 1,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("0")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_rate <- flextable::display(
  N_rate,
  i = 2,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("1")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_rate <- flextable::display(
  N_rate,
  i = 3,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("2")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_rate <- flextable::display(
  N_rate,
  i = 4,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("3")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_rate <- flextable::display(
  N_rate,
  i = 5,
  col_key = "rowname",
  pattern = "{{val}}{{pow}}",
  part = "body",
  formatters = list(val ~ as.character("N"), pow ~ as.character("4")),
  fprops = list(pow = fp_text(
    vertical.align = "subscript", font.size = 8
  ))
)

N_rate <- add_header(N_rate,
                           Year = "Year",
                           Tillering = "Application Rate (kg/ha)")

N_rate <- merge_v(N_rate, part = "header")

N_rate <- autofit(N_rate)
N_rate

```
